---
title: "Student Job Placement Analysis Report"
author: "Angelica Wright"
output: html_document
---

```{r setup, include=FALSE}
library(JobPlacementData)
library(ggplot2)
cleaned <- clean_placement(placement)
```

# Introduction

This report summarizes the analysis conducted using the **JobPlacementData** package. 
The goal is to explore how IQ, CGPA, internship completion, and college affiliation 
affect student job placement outcomes.

# Summary Statistics

```{r}
summarize_placement(cleaned)
```

### Placement Rate Formula



\[
\text{Placement Rate} = \frac{\text{Placed}}{\text{Total}}
\]



# Correlation Analysis

```{r}
correlation_matrix(cleaned)
```

### Correlation Formula



\[
r = \frac{\sum (x - \bar{x})(y - \bar{y})}
         {\sqrt{\sum (x - \bar{x})^2 \sum (y - \bar{y})^2}}
\]



# Visualizations

## Placement Rate by Internship

```{r}
plot_internship_placement_rate_ggplot(cleaned)
```

## Placement Rate by College

```{r}
plot_college_placement_rate_ggplot(cleaned)
```

## Placement Rate by IQ Group

```{r}
plot_iq_group_placement_rate_ggplot(cleaned)
```

## IQ × Internship × Placement (Grouped Boxplot)

```{r}
plot_iq_internship_placement_ggplot(cleaned)
```

# Interpretation

The bar charts show differences in placement rates across internship status, 
colleges, and IQ groups. The grouped boxplot highlights how IQ varies jointly with 
internship completion and placement outcome. This is a tool that could used with additional factors and contexts as needed for analysis. 

# Conclusion

This analysis demonstrates how simple visualizations and mathematical summaries 
can be used to explore predictors of job placement outcomes.
